---
title: "MiniRocket Vis"
author: "Kento Shigyo"
date: "11/9/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
install.packages("cowplot")
library(tidyverse)
library(dplyr)
library(stringr)
library(cowplot)
```

## Visualize dataset info
```{r}
# dataset_info_old <- read_csv("results_all.csv")
# dataset_info <- read_csv("results_new.csv")
dataset_info_correct <- read_csv("results_correct.csv")
```

## Dataset information
```{r}
x_labels_with_class_num <- dataset_info %>% 
  select(dataset_name, n_classes) %>% 
  mutate(x_labels=str_c(dataset_name, ":", n_classes)) %>% 
  pull(x_labels) %>% 
  unique()

dataset_info_correct %>% 
  arrange(size_train) %>% 
  filter(transformer_name=="minirocket") %>% 
  ggplot() +
  geom_bar(aes(x=dataset_name, y=size_test, fill=dataset_name), stat='identity')  +
  geom_bar(aes(x=dataset_name, y=size_train, alpha=0.3), stat="identity") +
  # scale_x_discrete(labels=x_labels_with_class_num) +
  scale_fill_discrete(labels=x_labels_with_class_num) +
  scale_alpha(labels = "training size") +
  ggtitle("Dataset Information") +
  labs(x="Dataset name", y="Testing size and training size in alpha", fill="Dataset:classes", alpha="Alpha") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  
```

# Visualization of the results with some datasets

## Transformation time with training data (our Mini Rocket vs our Rocket)

```{r}
dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket"))) %>%
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  filter(transformer_name %in% c("minirocket", "rocket")) %>% 
  # mutate(group = if_else(str_detect(transformer_name, pattern="minirocket"), "type_minirocket", "type_rocket")) %>% 
  ggplot() +
  geom_col(aes(x=dataset_name, y=time_transform_train, fill=transformer_name), stat='identity', position=position_dodge(0.8), width=0.8)  +
  scale_fill_manual(values=c("#01BFC4", "#F9766D")) +
  ggtitle("Transformation time with training data") +
  labs(x="Dataset name", y="Trasformation time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Transformation time with training data (our models vs the original models)xs

```{r}
g1 <- dataset_info_correct %>% 
  filter(transformer_name %in% c("minirocket", "sktimeminirocket")) %>% 
  mutate(transformer_name = factor(transformer_name, levels=c( "minirocket","sktimeminirocket"))) %>%
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot(mapping=aes(x=dataset_name, y=time_transform_train, fill=transformer_name)) +
  geom_col(stat='identity', position=position_dodge(0.8), width=0.8)  +
  scale_fill_manual(values=c("#01BFC4", "gray60")) +
  # scale_y_continuous(limits = c(0, 50)) +
  ggtitle("Transformation time with training data") +
  labs(x="Dataset name", y="Trasformation time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="top")

g2 <- dataset_info_correct %>% 
  filter(transformer_name %in% c("rocket", "sktimerocket")) %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("rocket", "sktimerocket"))) %>%
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot(mapping=aes(x=dataset_name, y=time_transform_train, fill=transformer_name)) +
  geom_col(stat='identity', position=position_dodge(0.8), width=0.8)  +
  scale_fill_manual(values=c("#F9766D", "gray60")) +
  ggtitle("Transformation time with training data") +
  labs(x="Dataset name", y="Trasformation time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="top") 

plot_grid(g1, g2, labels=c("", ""), ncol=1, nrow=2)
```


## Transformation time with training data (Mini Rocket family)
```{r}
g1 <- dataset_info_correct %>% 
  filter(transformer_name %in% c("rocket", "minirocket")) %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("minirocket", "rocket"))) %>%
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot(mapping=aes(x=dataset_name, y=time_transform_train, fill=transformer_name)) +
  geom_col(stat='identity', position=position_dodge(0.8), width=0.8) +
  scale_fill_manual(values=c("#01BFC4", "#F9766D")) +
  # scale_y_continuous(limits = c(0, 50)) +
  ggtitle("Transformation time with training data") +
  labs(x="Dataset name", y="Trasformation time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="top")

g2 <- dataset_info_correct %>% 
  filter(transformer_name %in% c("minirocket", "deterministicminirocket")) %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("minirocket", "deterministicminirocket"))) %>%
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot(mapping=aes(x=dataset_name, y=time_transform_train, fill=transformer_name)) +
  geom_col(stat='identity', position=position_dodge(0.8), width=0.8)  +
  scale_fill_manual(values=c("#01BFC4", "#FC813E")) +
  # scale_y_continuous(limits = c(0, 50)) +
  ggtitle("Transformation time with training data") +
  labs(x="Dataset name", y="Trasformation time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="top")



plot_grid(g1, g2, labels=c("", ""), ncol=1, nrow=2)
```



## Transformation time with testing data 
```{r}
dataset_info_correct %>% 
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot() +
  geom_bar(aes(x=dataset_name, y=time_transform_test, fill=transformer_name), stat='identity', position=position_dodge())  +
  ggtitle("Time for transformation with testing data") +
  labs(x="Dataset name", y="Time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

## Transformation time with training data 2
```{r}
dataset_info_correct %>% 
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot() +
  geom_bar(aes(x=dataset_name, y=time_transform_train, fill=transformer_name), stat='identity')  +
  # geom_bar(aes(x=dataset_name, y=time_transform_test, fill=transformer_name), stat='identity', position=position_dodge())  +
  ggtitle("Time for transformation with training data") +
  labs(x="Dataset name", y="Time", fill="Transformer name") +
  facet_wrap(~transformer_name, ncol=1)+
  # facet_grid(dataset_name ~ . )
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
## Transformation time with testing data 2
```{r}
dataset_info_correct %>% 
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test) %>% 
  ggplot() +
  geom_bar(aes(x=dataset_name, y=time_transform_test, fill=transformer_name), stat='identity')  +
  # geom_bar(aes(x=dataset_name, y=time_transform_test, fill=transformer_name), stat='identity', position=position_dodge())  +
  ggtitle("Time for transformation with testing data") +
  labs(x="Dataset name", y="Time", fill="Transformer name") +
  facet_wrap(~transformer_name, ncol=1)+
  # facet_grid(dataset_name ~ . )
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
# Training time
```{r}
dataset_info_correct %>% 
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test, time_train, time_total) %>% 
  ggplot() +
  # geom_bar(aes(x=dataset_name, y=time_total, fill=transformer_name), stat='identity')  +
  geom_col(aes(x=dataset_name, y=time_train, fill=transformer_name), stat='identity', position=position_dodge(0.5), width=0.8)  +
  ggtitle("Training time") +
  labs(x="Dataset name", y="Time", fill="Transformer name") +
  # facet_wrap(~transformer_name, ncol=1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
g1 <- dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket"))) %>%
  select(dataset_name, transformer_name,  time_train) %>% 
  mutate(group = if_else(str_detect(transformer_name, pattern="minirocket"), "type_minirocket", "type_rocket")) %>%
  filter(group == "type_minirocket") %>% 
  ggplot(mapping=aes(x=dataset_name, y=time_train, fill=transformer_name)) +
  geom_col(stat='identity', position=position_dodge(0.8), width=0.5)  +
  scale_fill_manual(values=c("gray60", "#01BFC4")) +
  # scale_y_continuous(limits = c(0, 65)) +
  ggtitle("Training time") +
  labs(x="Dataset name", y="Training time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # theme(axis.title.x = element_blank(), axis.text.x = element_blank())

g2 <- dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket"))) %>%
  select(dataset_name, transformer_name,  time_train) %>% 
  mutate(group = if_else(str_detect(transformer_name, pattern="minirocket"), "type_minirocket", "type_rocket")) %>%
  filter(group == "type_rocket") %>% 
  ggplot(mapping=aes(x=dataset_name, y=time_train, fill=transformer_name)) +
  geom_col(stat='identity', position=position_dodge(0.8), width=0.8)  +
  scale_fill_manual(values=c("gray60", "#F9766D")) +
  # scale_y_continuous(limits = c(0, 65)) +
  ggtitle("Training time") +
  labs(x="Dataset name", y="Training time", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

plot_grid(g1, g2, labels=c("", ""), ncol=1, nrow=2)
```


## Total time
```{r}
dataset_info_correct %>% 
  select(dataset_name, transformer_name,  time_transform_train, time_transform_test, time_train, time_total) %>% 
  ggplot() +
  # geom_bar(aes(x=dataset_name, y=time_total, fill=transformer_name), stat='identity')  +
  geom_bar(aes(x=dataset_name, y=time_total, fill=transformer_name), stat='identity', position=position_dodge())  +
  ggtitle("Total time") +
  labs(x="Dataset name", y="Time", fill="Transformer name") +
  # facet_wrap(~transformer_name, ncol=1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Classifier Score
```{r}
dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket", "deterministicminirocket"))) %>%
  select(dataset_name, transformer_name,  classifier_score) %>% 
  # filter(transformer_name %in%  c("minirocket", "rocket")) %>%
  filter(transformer_name %in%  c("deterministicminirocket", "minirocket")) %>%
  ggplot() +
  geom_col(aes(x=dataset_name, y=classifier_score, fill=transformer_name), stat='identity', position=position_dodge(0.8), width=0.8) +
  scale_fill_manual(values=c("#01BFC4", "#F9766D")) +
  guides(fill=guide_legend(reverse = TRUE)) +
  ggtitle("Classifier scores of transformers") +
  labs(x="Dataset Name", y="Classifier Score", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip() 


```


```{r}
g1 <- dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket"))) %>%
  mutate(group = if_else(str_detect(transformer_name, pattern="minirocket"), "type_minirocket", "type_rocket")) %>%
  filter(group == "type_minirocket") %>%
  select(dataset_name, transformer_name,  classifier_score) %>% 
  ggplot() +
  geom_col(aes(x=dataset_name, y=classifier_score, fill=transformer_name), stat='identity', position=position_dodge(0.8), width=0.8) +
  scale_fill_manual(values=c("gray60", "#01BFC4", "gray60", "#F9766D")) +
  guides(fill=guide_legend(reverse = FALSE)) +
  ggtitle("Classifier score of transformers") +
  labs(x="Dataset Name", y="Classifier Score", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="top") +
  coord_flip() 

g2 <- dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket"))) %>%
  mutate(group = if_else(str_detect(transformer_name, pattern="minirocket"), "type_minirocket", "type_rocket")) %>%
  filter(group == "type_rocket") %>%
  select(dataset_name, transformer_name,  classifier_score) %>% 
  ggplot() +
  geom_col(aes(x=dataset_name, y=classifier_score, fill=transformer_name), stat='identity', position=position_dodge(0.8), width=0.8) +
  scale_fill_manual(values=c("gray60", "#F9766D")) +
  guides(fill=guide_legend(reverse = TRUE)) +
  ggtitle("Classifier score of transformers") +
  labs(x="Dataset Name", y="Classifier Score", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.y = element_blank(), legend.position="top") +
  # theme(axis.text.y = element_blank(), axis.title.y = element_blank(), legend.position="top") +
  coord_flip() 

plot_grid(g1, g2, labels=c("", ""), ncol=2, nrow=1)
```

```{r}
score_rocket_minirocket <- dataset_info_correct %>% 
  mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket"))) %>%
  # mutate(group = if_else(str_detect(transformer_name, pattern="minirocket"), "type_minirocket", "type_rocket")) %>%
  # filter(group == "type_minirocket") %>%
  filter(transformer_name %in% c("rocket", "minirocket")) %>% 
  select(dataset_name, transformer_name,  classifier_score) %>% 
  ggplot() +
  geom_col(aes(x=dataset_name, y=classifier_score, fill=transformer_name), stat='identity', position=position_dodge(0.8), width=0.8) +
  scale_fill_manual(values=c("#01BFC4", "#F9766D")) +
  guides(fill=guide_legend(reverse = FALSE)) +
  ggtitle("Classifier score of transformers") +
  labs(x="Dataset Name", y="Classifier Score", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  legend.position="top", axis.title.y = element_blank()) +
  coord_flip() 

score_deter_mini <- dataset_info_correct %>% 
   mutate(transformer_name = factor(transformer_name, levels=c("sktimeminirocket", "minirocket", "sktimerocket", "rocket", "deterministicminirocket"))) %>%
  filter(transformer_name %in% c("deterministicminirocket", "minirocket")) %>% 
  select(dataset_name, transformer_name,  classifier_score) %>% 
  ggplot() +
  geom_col(aes(x=dataset_name, y=classifier_score, fill=transformer_name), stat='identity', position=position_dodge(0.8), width=0.8) +
  scale_fill_manual(values=c("#01BFC4", "#FC813E")) +
  guides(fill=guide_legend(reverse = FALSE)) +
  ggtitle("Classifier score of transformers") +
  labs(x="Dataset Name", y="Classifier Score", fill="Transformer name") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="top") +
  coord_flip() 

plot_grid(score_rocket_minirocket, score_deter_mini, labels=c("A", "B"), ncol=2, nrow=1)

```



```{r}
size_train <-  dataset_info %>% 
  filter(transformer_name == "minirocket") %>% 
  select(size_train)

dataset_name <- dataset_info %>% filter(transformer_name == "minirocket") %>% select(dataset_name)

time_transform_minirocket <- dataset_info %>% 
  filter(transformer_name == "minirocket") %>% 
  rename(y = time_transform_train) %>% 
  select(y)

time_transform_sktimerocket <- dataset_info %>% 
  filter(transformer_name == "sktimerocket") %>% 
  rename(x = time_transform_train) %>% 
  select(x)

time_transform_deterministicminirocket <- dataset_info %>% 
  filter(transformer_name == "deterministicminirocket") %>% 
  rename(x = time_transform_train) %>% 
  select(x)

time_transform_rocket <- dataset_info %>% 
  filter(transformer_name == "rocket") %>% 
  rename(x = time_transform_train) %>% 
  select(x)
  
a <-data.frame(x=time_transform_rocket, y=time_transform_minirocket, size_train = size_train) %>%
  mutate(is_better = if_else( y < x, TRUE, FALSE))
dummy <- data.frame(-10, -10, 200, FALSE)
names(dummy) <- c("x", "y", "size_train", "is_better")
a <- rbind(a, dummy)

  
ggplot(data=a, aes(x=x, y=y)) +
  geom_point(aes(size=size_train, color=is_better),  alpha=0.3) +
  scale_color_manual(values=c("red", "blue"), labels=c("False", "True"), drop=FALSE, name="Mini Rocket is better") +
  xlim(0, 30) + ylim(0, 30) +
  # xlim(0, 3) + ylim(0, 3) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("Tansformation time with training data") +
  labs(x="Transformation time of our Rocket", y="Transformation time of our Mini Rocket", size="Training size")
```




